---
title: "R Notebook"
output: html_notebook
---

# Creating the environment

```{r}
library(tidyverse)
library(lavaan)
```

Note: please check this course

https://app.datacamp.com/learn/courses/survey-and-measurement-development-in-r 
https://s3.amazonaws.com/assets.datacamp.com/production/course_17043/slides/chapter3.pdf 


# Loading data

```{r}
mlm_ent <- 
  read_csv("https://docs.google.com/spreadsheets/d/1b-bKoYI2jpMnTe2ae1rMaQuCrn3IadFq5MEtiwZwAEE/export?format=csv&gid=1178976425") |> 
  select(Q16, Q17, Q18, # tie strength
         Q19, Q20, Q21, # Satisfaction
         Q22, Q23, # Monetary Incentive
         Q24, Q25, Q26, Q28) # Recommendation
  
```

# Exploratory Factor Analysis (EFA)

Source:

https://play.google.com/books/reader?id=MkbHCgAAAEAJ&pg=GBS.PA256.w.0.0.0.3_61


https://s3.amazonaws.com/assets.datacamp.com/production/course_17043/slides/chapter2.pdf


# Data tidying

```{r}
mlm_ent_sc <- mlm_ent
mlm_ent_sc <- scale(mlm_ent)
summary(mlm_ent_sc)
```


## Finding an EFA solution

```{r}
eigen(cor(mlm_ent_sc))
```

```{r}
factanal(mlm_ent_sc, factors = 4)
```

Factor 1: Satisfaction (Q19, Q20, Q21)
Factor 2: Recommendation (Q24, Q26, Q25, Q28) 
Factor 3: Tie Strength (Q16, Q17, Q18)
Factor 4: Monetary Incentives (Q22, Q23)

With oblimin rotation

```{r}
(mlm_ent_fa_ob <- factanal(mlm_ent_sc, factors = 4, rotation = "promax"))
```

< 0.39 pobre
.4 - .49 Justo
.5 - .59 Bueno
.6 - .69 Muy bueno 
.7 + Excelente

Path visualization

```{r}
library(semPlot)
semPaths(mlm_ent_fa_ob, 
         what = "est", 
         residuals = FALSE, 
         cut = 0.3, 
         posCol = c("white", "darkgreen"), 
         negCol = c("white", "red"), 
         edge.label.cex = 0.75, 
         nCharNodes = 7)
```
Loadings < 0.3 are excluded. 

# Confirmatory Factor Analysis 

## Model 

```{r}
mlm_model <- 
              "# Measurement Model
               Satisfaction =~ Q19 + Q20 + Q21
               Monetary_incentive =~ Q22 + Q23
               Tie_strenght =~ Q16 + Q17 + Q18
               Recommendation =~ Q24 + Q28 + Q25 + Q26 
               # Regressions
               Monetary_incentive ~ Satisfaction 
               Tie_strenght ~ Satisfaction
               Recommendation ~ Satisfaction + Tie_strenght + Monetary_incentive"
```

```{r}
library(lavaan)
library(semTools)
library(semPlot)
```

# Model Estimation

```{r}
mlm_fit <- cfa(mlm_model, data = mlm_ent)
summary(mlm_fit, fit.measures = TRUE)
```

The four hierarchical model fits the data well. Fit indices are strong (CFI = 0.956) residuals are low (RMSEA = 0.091). All latent variables are significant (p-valor < 0.05). are similiar to one another in magnitude (ranging 0.847 - 1.363) 

Ploting the model 

```{r}
library(semPlot)
semPaths(mlm_fit, 
         what = "est", 
         fade = FALSE, 
         residuals = FALSE, 
         edge.label.cex = 0.75)
```

               Monetary_incentive ~ Satisfaction 
               Tie_strenght ~ Satisfaction
               Recommendation ~ Satisfaction + Tie_strenght + Monetary_incentive"

```{r}
reliability(mlm_fit)
```

```{r}
inspect(mlm_fit, what = "std")$lambda
```

## Correlation matrix 

```{r}
TS <- mlm_ent |> 
  rowwise() |> 
  mutate(TS = mean(Q16, Q17, Q18))

SAT <- mlm_ent |> 
  rowwise() |> 
  mutate(SAT = mean(Q19, Q20, Q21))

MI <- mlm_ent |> 
  rowwise() |> 
  mutate(MI = mean(Q22, Q23))

REC <- mlm_ent |> 
  rowwise() |> 
  mutate(REC = mean(Q24, Q25, Q26, Q28))

mlm_latent <- 
  tibble(TS = TS$TS,
         SAT = SAT$SAT,
         MI = MI$MI,
         REC = REC$REC)

rcorr(as.matrix(mlm_latent))
```


Latent variables

https://www.youtube.com/watch?v=eLDrF3vwyXc

```{r}
RE <- nataliaSimData |> 
  rowwise() |> 
  mutate(RE = mean(i1, i2, i3)) 

DE <- nataliaSimData |> rowwise() |> mutate(DE = mean(i4, i5, i6))
CD <- nataliaSimData |> rowwise() |> mutate(CD = mean(i7, i8, i9))

natalia_latent <- 
  tibble(RE = RE$RE,
         DE = DE$DE,
         CD = CD$CD)

rcorr(as.matrix(natalia_latent))
```


```{r}
lavInspect(mlm_fit, "cor.lv")
```

## Covariance matrix

```{r}
fitted(sem(mlm_fit))
```


```{r}
round(cor(mlm_ent), digits = 2)
```

With p-values

```{r}
rcorr(as.matrix(mlm_ent))
```


# Tables

## Table 1 Descriptive statistics 

```{r}

```


## Table 2 Correlation Matrix

https://www.researchgate.net/post/How-to-extract-correlation-matrix-of-latent-variables-in-lavaan-hierarchical-CFA-Why-does-corlavPredictfit-differ-from-lavInspectfit-corlv

```{r}
lavInspect(mlm_fit, "cor.lv")
```


