---
title: "R Notebook"
output: html_notebook
---

# Creating the environment

```{r}
library(tidyverse)
library(lavaan)
```

Note: please check this course

https://app.datacamp.com/learn/courses/survey-and-measurement-development-in-r 
https://s3.amazonaws.com/assets.datacamp.com/production/course_17043/slides/chapter3.pdf 


# Loading data

```{r}
mlm_ent <- 
  read_csv("https://docs.google.com/spreadsheets/d/1b-bKoYI2jpMnTe2ae1rMaQuCrn3IadFq5MEtiwZwAEE/export?format=csv&gid=1178976425") |> 
  select(Q16, Q17, Q18, # tie strength
         Q19, Q20, Q21, # Satisfaction
         Q22, Q23, # Monetary Incentive
         Q24, Q25, Q26, Q28) # Recommendation
  
```

# Exploratory Factor Analysis (EFA)

Source:

https://play.google.com/books/reader?id=MkbHCgAAAEAJ&pg=GBS.PA256.w.0.0.0.3_61

# Data tidying

```{r}
mlm_ent_sc <- mlm_ent
mlm_ent_sc <- scale(mlm_ent)
summary(mlm_ent_sc)
```


## Finding an EFA solution

```{r}
eigen(cor(mlm_ent_sc))
```

```{r}
factanal(mlm_ent_sc, factors = 4)
```

Factor 1: Satisfaction (Q19, Q20, Q21)
Factor 2: Recommendation (Q24, Q26, Q25, Q28) 
Factor 3: Tie Strength (Q16, Q17, Q18)
Factor 4: Monetary Incentives (Q22, Q23)

With oblimin rotation

```{r}
(mlm_ent_fa_ob <- factanal(mlm_ent_sc, factors = 4, rotation = "promax"))
```

Path visualization

```{r}
library(semPlot)
semPaths(mlm_ent_fa_ob, 
         what = "est", 
         residuals = FALSE, 
         cut = 0.3, 
         posCol = c("white", "darkgreen"), 
         negCol = c("white", "red"), 
         edge.label.cex = 0.75, 
         nCharNodes = 7)
```
Loadings < 0.3 are excluded. 

# Confirmatory Factor Analysis 

## Model 

```{r}
mlm_model <- 
              "Satisfaction =~ Q19 + Q20 + Q21
               Monetary_incentive =~ Q22 + Q23
               Tie_strenght =~ Q16 + Q17 + Q18
               Recommendation =~ Q24 + Q28 + Q25 + Q26 
               Monetary_incentive ~ Satisfaction 
               Tie_strenght ~ Satisfaction
               Recommendation ~ Satisfaction + Tie_strenght + Monetary_incentive"
```

```{r}
library(lavaan)
library(semTools)
library(semPlot)
```

# Model Estimation

```{r}
mlm_fit <- cfa(mlm_model, data = mlm_ent)
summary(mlm_fit, fit.measures = TRUE)
```

The four hierarchical model fits the data well. Fit indices are strong (CFI = 0.956) residuals are low (0.091). All laten variables are significant (p-valor < 0.05). are similiar to one another in magnitude (ranging 0.847 - 1.363) 

Ploting the model 

```{r}
library(semPlot)
semPaths(mlm_fit, what = "est", fade = FALSE, residuals = FALSE, edge.label.cex = 0.75)
```

```{r}
reliability(mlm_fit)
```

```{r}
inspect(mlm_fit, what = "std")$lambda
```

## Correlation matrix 

```{r}
cov2cor(inspect(mlm_fit, what = "est")$psi)
```

```{r}
round(cor(mlm_ent), digits = 2)
```

# Tables

## Table 1 

Descriptive statistics 

```{r}

```



## 